miceafterFA

### 2024-03-10 miceafterfa.Rmd
made lms with mice

---
title: "models with mice"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

@@

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(Hmisc))
suppressPackageStartupMessages(library(reshape2))

@@

## Can do something with accept, reject and reluctantly accept.

@@

## Can do something with accept, reject and reluctantly accept.

n_acceptreject<- codedmodule2 %>%
                dplyr::select("N_accept", "N_reluctantlyaccept", "N_reject")

summary(n_acceptreject)
```

@@

formice <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext"))

@@

library(dplyr)

formice <- formice %>%
  mutate(across(Risky_Solar:age, ~factor(.x, ordered = TRUE)))%>%
  mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
  mutate(across(State, ~factor(.x, ordered = FALSE)))

str(formice)
summary(formice)

## Mifa for Kahan scale 
```{r, echo =FALSE}
library(mifa)
library(mice)
library(psych)

 #cov_vars = -c(State, Risky_Solar, Risky_Nuclear, Risky_Coal, Ben_Solar, Ben_Nuclear, Ben_Coal, DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE, ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB, OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION, DISPLACESOLAR, POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR, PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR, RELYSOLAR, DISPLACECOAL, POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL, PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL, RELYCOAL, DISPLACENUCLEAR, POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR, PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR, RELYNUCLEAR, age, urban_rural, gender, caste, religion),

kahanall <- codedmodule2 %>%
          dplyr::select(c(starts_with("K_")))

mikahan <- mifa(data= kahanall,
                cov_vars = everything(),
                m = 10,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 427,)

mikahan

library(psych)

fit <- psych::fa(mikahan$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(fit, sort= TRUE, cut= 0.4)

data_imp <- mice::complete(mice::mice(kahanall, 1, print = FALSE))

fct_scores <- data.frame(factor.scores(data_imp[, 1:12], fit)$scores)

#checking imputations: Kahan scale

orgscores <- data.frame(kahanefascores)

summary(mikahan)
names(mikahan)

mikahan$mids

complete_data_first <- complete(mikahan$mids, 1)

summary(complete_data_first)

complete_data_2 <- complete(mikahan$mids, 2)

summary(complete_data_2)

complete_data_3 <- complete(mikahan$mids, 3)

summary(complete_data_3)

complete_data_4 <- complete(mikahan$mids, 4)

summary(complete_data_4)

complete_data_5 <- complete(mikahan$mids, 5)

summary(complete_data_5)
```

## Distribution check: kahan Scale

```{r}
# Add an identifier column to each dataset
fct_scores$Dataset <- 'fct_scores'
orgscores$Dataset <- 'orgscores'

# Combine the datasets for plotting
combined_data <- rbind(fct_scores, orgscores)

# Select only necessary columns (assuming 'Index' isn't needed anymore)
combined_data <- combined_data[, c("MR1", "MR2", "Dataset")]

ggplot(combined_data, aes(x = Dataset, y = MR1, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of MR1 for Each Dataset", x = "", y = "MR1 Value") +
  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  theme_minimal()

ggplot(combined_data, aes(x = MR1, color = Dataset)) +
  geom_density(fill = NA, alpha = 0.5) +
  labs(title = "Density Plot of MR1 for Each Dataset", x = "MR1 Value", y = "Density") +
  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  theme_minimal()

```
```{r}
ggplot(combined_data, aes(x = Dataset, y = MR2, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of MR2 for Each Dataset with Points", x = "", y = "MR2 Value") +
  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  theme_minimal()

# Mifa for new eco-pol value scale : Nuclear energy

ecopoln <- codedmodule2[, grep("NUCLEAR|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]

miecopol <- mifa(data= ecopoln,
                cov_vars = everything(),
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 429,)

miecopol

fit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(fit2, sort= TRUE, cut= 0.4)

data_imp2 <- mice::complete(mice::mice(ecopoln, 1, print = FALSE))

fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:23], fit2)$scores)

## Checking imputations : Eco-pol scale

summary(miecopol)
names(miecopol)

miecopol$mids

complete_ecopol_first <- complete(miecopol$mids, 1)

summary(complete_ecopol_first)

complete_ecopol_2 <- complete(miecopol$mids, 2)

summary(complete_ecopol_2)

complete_ecopol_3 <- complete(miecopol$mids, 3)

summary(complete_ecopol_3)

complete_ecopol_4 <- complete(miecopol$mids, 4)

summary(complete_ecopol_4)

complete_ecopol_5 <- complete(miecopol$mids, 5)

summary(complete_ecopol_5)

@@

nscores <- data.frame(ecopolall_scores$scores)

# Add an identifier column to each dataset
fct_scores2$Dataset <- 'imputed'
nscores$Dataset <- 'original'

# Combine the datasets for plotting
compare2 <- rbind(fct_scores2, nscores)

# Select only necessary columns (assuming 'Index' isn't needed anymore)
compare2<- compare2[, c("MR1", "MR2", "Dataset")]

ggplot(compare2, aes(x = Dataset, y = MR1, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of Pdevelop for Each Dataset", x = "", y = "MR1 Value") +
  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
  theme_minimal()

@@

ggplot(compare2, aes(x = Dataset, y = MR2, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of Ndevelop for Each Dataset with Points", x = "", y = "MR2 Value") +
  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
  theme_minimal()

@@

library(ggplot2)

ggplot(compare2, aes(x = MR2, color = Dataset)) +
  geom_density(fill = NA, alpha = 0.5) +
  labs(title = "Density Plot of MR2 for Each Dataset", x = "MR2 Value", y = "Density") +
  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
  theme_minimal()

# Binding imputed values to formice dataset

```{r, echo = FALSE}

# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2

ecopolnuclear <- fct_scores2 %>%
  rename(Pdevelop = MR1, Ndevelop = MR2)

kahannuclear <- fct_scores%>%
  rename(Communitarian_Egalitarian = MR1, Hierarchy = MR2)

nuclearformice <- cbind(formice, kahannuclear, ecopolnuclear) %>%
                  dplyr::select(-c(Dataset))

>>>>

---
title: "miceafterFA"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

@@

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(Hmisc))
suppressPackageStartupMessages(library(reshape2))
suppressPackageStartupMessages(library(naniar))
suppressPackageStartupMessages(library(mice))

@@

@@

codedmodule2$State <- as.factor(codedmodule2$State)
codedmodule2$gender <- as.factor(codedmodule2$gender)
codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
codedmodule2$caste <- as.factor(codedmodule2$caste)
codedmodule2$religion <- as.factor(codedmodule2$religion)
# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)
```

# missing data pattern and MCAR

@@

formice1 <- codedmodule2[, grep("State|age|Urban|Male|Uppercaste|Hindu|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar")) %>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))

@@

#str(formice)
#summary(formice)

# litte's MCAR test

mcar_test(data=formice1)

# p value = 1, which means MAR condition is met.

@@

Kahan_scale <- codedmodule2 %>%
  dplyr::select(starts_with("K_"))

# EFA on Kahan scale

kahan.fa <- fa(Kahan_scale, nfactors = 2, rotate = "varimax")
print.psych(kahan.fa, cut = 0.4, sort = TRUE)

# extract factor scores

Kahanefa <- psych::factor.scores(Kahan_scale, kahan.fa)

# The factor scores will be stored in the scores element of the returned list
kahanefascores <- data.frame(Kahanefa$scores) %>%
  rename(CommEgal = MR1)%>%
  rename(Hierarchy = MR2)

library(psych)
library(tidyverse)

ecopolall <- codedmodule2 %>%
        dplyr::select("WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")

# running EFA using psych package

ecopolall2.fa <- fa(ecopolall, nfactors = 2, rotate = "varimax")

print.psych(ecopolall2.fa, sort = TRUE)

# the two factors make more sense - 1) people centered development 2) nationalist development
# So I am going to extract factor scores and bind them to the dataset

ecopolall_scores <- psych::factor.scores(ecopolall, ecopolall2.fa)

# The factor scores will be stored in the scores element of the returned list
scores1 <- data.frame(ecopolall_scores$scores) %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2)

#binding factor scores to the dataset

premice <- cbind (formice1, kahanefascores, scores1) %>%
          dplyr::select(-c(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE, ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB, OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION, DISPLACESOLAR, POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR, PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR, RELYSOLAR, DISPLACECOAL, POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL, PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL, RELYCOAL))

```{r}
# conducting mice

postmice <- mice(premice, m =5, maxit =5,  seed = 420, print = FALSE)

summary(postmice)

complete(postmice)

fit <- with(postmice, lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ CommEgal + Hierarchy + Pdevelop + Ndevelop))

summary(pool(fit))

@@

@@
